---
title: "Advanced Statistics Assignment"
author: "Bruno Lenderink, Fabiana Caccavale, Marco Amadori, Lisa Aita"
date: "November 10, 2021"
output:
  pdf_document: default
---

# temporary description of project

Import then into R the attached data. 

Provide descriptives of relevant variables and associations in the data. 
Select then G3 as your target variable, and provide a linear regression model to predict it. Do not use G1 or G2 as potential predictors. 
Interpret the results of your final model, and assess its predictive performance. 
Your deliverables are a 2-3 page report (not counting tables and figures), and a replication package in the form of data and 
a text file with R code that I can copy and paste to reproduce your analysis. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)

```



#To remove all the objects that are stored in your global environment (but not remove any of loaded packages):

```{r, include=FALSE}
if(!is.null(dev.list())) dev.off()
cat("\014") 
rm(list = ls())
```

#Packages
#To put all packages (that were previously installed) into memory:




```{r Library and data imports,include=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
#Libraries
library(stargazer)
library(dplyr)
library(knitr)
library(readr)
library(tidyverse)
library(MASS)

#Dataset
dataset = read.csv("student-por.csv", sep = ";", header = TRUE)
#Check for missing values
sum(is.na(dataset))
```

```{r Explore data, results = "asis"}

stargazer(dataset, header=FALSE, type='latex', title="Descriptive statistics")


```
```{r Preparing data}

```

```{r Linear Regression, , include=FALSE}
#First we simply run a linear regression of G3 on all variables except G1 and G2
model <- lm(G3 ~ . - G1 - G2 ,
             data = dataset)


modAIC=stepAIC(lm(G3 ~ . - G1 - G2,
             data = dataset),direction="both")

```
```{r Linear Regression results, results='asis',echo=FALSE}

stargazer(model, header=FALSE, single.row = TRUE, title='Regression results using all variables')
stargazer(modAIC, header=FALSE, single.row = TRUE, title="Regression results using AIC")
```
```{r Train test split, results='asis'}
w <- sample(nrow(dataset), nrow(dataset)*0.8)
trainmodel <- lm(G3 ~ school + sex + age + Medu + guardian + studytime + failures + 
    schoolsup + higher + romantic + Dalc + health + absences, data=dataset[w,])
stargazer(trainmodel, header=FALSE, single.row = TRUE, title="Regression model using AIC selected variables on only training data")
pr.test=predict(trainmodel,newdata=dataset[-w,])
print(mean((dataset$G3[-w]-pr.test)^2))


```

```{r Graph, fig.show='hide'}
plot(G3 ~ age , data=dataset,
   xlab="Age", ylab="Score",
   main="Enhanced Scatter Plot"
   )
```

